---
title: "HW6"
author: "Caden McQuillen"
date: '2023-02-15'
output:
  html_document:
    toc: yes
---
## Library
```{r,message=FALSE }
library(dplyr)
library(ggplot2)
library(stringr)

```

## Question 1
```{bash, eval=FALSE}
#get WT1 fastqc files
scp cnm4001@aphrodite.med.cornell.edu:/home/cnm4001/angsd_hw/hw4/WT1/ERR458493_fastqc/fastqc_data.txt .
mv fastqc_data.txt WT1_ERR458493_fastqc_data.txt
scp cnm4001@aphrodite.med.cornell.edu:/home/cnm4001/angsd_hw/hw4/WT1/ERR458494_fastqc/fastqc_data.txt .
mv fastqc_data.txt WT1_ERR458494_fastqc_data.txt
#get SNF2_1 fastqc files
scp cnm4001@aphrodite.med.cornell.edu:/home/cnm4001/angsd_hw/hw4/SNF2_1/ERR458500_fastqc/fastqc_data.txt .
mv fastqc_data.text SNF2_1_ERR458500_fastqc_data.txt
scp cnm4001@aphrodite.med.cornell.edu:/home/cnm4001/angsd_hw/hw4/SNF2_1/ERR458501_fastqc/fastqc_data.txt .
mv fastqc_data.text SNF2_1_ERR458501_fastqc_data.txt


```

## Question 2
```{r}

#' Function for parsing the text output of FastQC
#'
#' This functions extracts the values for a specific test run by FastQC on a
#' single fastq file.
#'
#' @param file string that specifies the path to an individual FastQC result file
#' (typically named "fastqc_data.txt"
#' @param test Indicate which test results should be extracted. Default:
#' "Per base sequence quality". Other options are, for example, "Per tile sequence quality",
#' "Per sequence quality score" etc.
#'
#' @return data.frame with the values of a single FastQC test result.
#'
#' @examples \dontrun{
#' my_result <- parse_fastqc(file = "fastqc_data.txt") 
#' 

parse_fastqc <- function(file, samplename, test = "Per base sequence quality") {

  # generate the string that will be used for the file parsing
  syscommand <- paste0("sed -n '/", test, "/,/END_MODULE/p' ", file, " | grep -v '^>>'")

  # use the fread command, which can interpret UNIX commands on the fly to
  # read in the correct portion of the FastQC result
  fastqc_data <- data.table::fread( cmd = syscommand, header = TRUE) %>% as.data.frame
  
  return(fastqc_data)
}

setwd("/Users/Caden/Desktop/angsd/hw6")
WT1_ERR458493 <-parse_fastqc(file = "WT1_ERR458493_fastqc_data.txt", test = "Per base sequence quality")

```
## Question 3
syscommand <- paste0("sed -n '/", test, "/,/END_MODULE/p' ", file, " | grep -v '^>>'") <br/>

This sed command is extracting lines in between a range of patterns <br/>
test is the pattern at the start of the range, where test is "Per base sequence quality" but can be specified by function user <br/>
"END_MODULE" is end pattern <br/>
p writes the pattern space to standard output <br/>
-n command disables automatic printing of lines that match the pattern<br/>

## Question 4 & 5
```{r}
#' Function for parsing the text output of FastQC
#'
#' This functions extracts the values for a specific test run by FastQC on a
#' single fastq file.
#'
#' @param file string that specifies the path to an individual FastQC result file
#' (typically named "fastqc_data.txt"
#' @param test Indicate which test results should be extracted. Default:
#' "Per base sequence quality". Other options are, for example, "Per tile sequence quality",
#' "Per sequence quality score" etc.
#'
#' @return data.frame with the values of a single FastQC test result.
#'
#' @examples \dontrun{
#' my_result <- parse_fastqc(file = "fastqc_data.txt") 
#' 

parse_fastqc <- function(file, samplename, test = "Per base sequence quality") {

  # generate the string that will be used for the file parsing
  syscommand <- paste0("sed -n '/", test, "/,/END_MODULE/p' ", file, " | grep -v '^>>'")

  # use the fread command, which can interpret UNIX commands on the fly to
  # read in the correct portion of the FastQC result
  fastqc_data <- data.table::fread( cmd = syscommand, header = TRUE) %>% as.data.frame
  fastqc_data$sampleName <- samplename
  return(fastqc_data)
}

setwd("/Users/Caden/Desktop/angsd/hw6")

WT1_ERR458493 <-parse_fastqc(file = "WT1_ERR458493_fastqc_data.txt", samplename = "WT1_ERR458493", test = "Per base sequence quality")

#########################Question 5##############################
#get list of files in current directory
rm(WT1_ERR458493)
file_list <- list.files()
for (file in file_list){
  filename <- str_split_1(file, pattern = "_fastqc_data.txt")
  assign(paste0(filename[1],"_df"),parse_fastqc(file = file, samplename = filename[1], test = "Per base sequence quality"))
}


```
## Question 6
```{r}
```


```{r}
final_df <- rbind(SNF2_1_ERR458500_df,SNF2_1_ERR458501_df)
final_df <- rbind(final_df,WT1_ERR458493_df)
final_df <- rbind(final_df,WT1_ERR458494_df)

```
## Question 7
```{r}
colnames(final_df)[1]<- "Base"
final_df[c('Condition', 'Sample')] <- str_split_fixed(final_df$sampleName, '_', 2)
final_df <- final_df %>% 
  mutate(Sample = str_replace(Sample,"1_", ""))
final_df <- final_df %>% 
  mutate(Condition = str_replace(Condition,"1", ""))

ggplot(final_df, aes(x = Base, y = Mean, colour = Sample)) + facet_grid(.~Condition)+
  geom_point(stat="identity")+ylim(0,45)
```

## Question 8
```{r}
sessionInfo()
```

